---
title: "Final Report for Intro to Data Science"
output: html_notebook
---
Robert Guenther
Github- https://github.com/rguenther23/final_project_ds

# Intro
The Data set I chose was the BillBoard top 100. I got this data from the github repo Professor Sanchez provided us with.
I used 'ggplot2' and 'tidyverse' to try to find out:
How many songs were by Elvis, How many have features, and How many are Explicit.
```{r}
library(tidyverse)
```

```{r}
summer_hits_URL <- "https://raw.githubusercontent.com/reisanar/datasets/master/bbTop100.csv"
summer_hits <- read.csv(summer_hits_URL)
summer_hits
```

```{r}
library(ggplot2)
```
# Question 1
How many songs are by Elvis?
```{r}
has_Elvis <- summer_hits %>% 
  mutate(
      contains_Elvis = case_when(
      str_detect(artist_name, "Elvis") ~ "yes", 
      TRUE ~ "No"))
has_Elvis
```

```{r}
ggplot(has_Elvis) +
  geom_col(aes(x = contains_Elvis, y = 1, color = contains_Elvis)) +
  labs(title = "Songs Containing by Elvis VS the Songs that aren't", x = "Tracks", y = "Number of Songs")
```

```{r}
has_Elvis %>% 
  filter(contains_Elvis == "yes")
```
# Question 2
How many songs have features?
```{r}
featured <- summer_hits %>%
  filter(str_detect(artist_name,"featuring"))
featured
```
# Question 3
How many Explicit songs are on the top 100?
```{r}
has_Explicit <- summer_hits %>% 
  mutate(
      contains_Explicit = case_when(
      str_detect(explicit, "true") ~ "yes", 
      TRUE ~ "No"))
has_Explicit
```

```{r}
ggplot(has_Explicit) +
  geom_col(aes(x = contains_Explicit, y = 1, color = contains_Explicit)) +
  labs(title = "Explicit Vs Non-Explicit songs", x = "Tracks", y = "Number of Songs")
```
Suprisingly there was only no explicit songs.
